---
title: "FDA Legitimacy: conjoint pilot results"
date: '2024-09-22'
output: 
  html_document:
  code_folding: hide
highlight: tango
number_sections: yes
theme: united
toc: yes
toc_depth: 4
toc_float: yes
urlcolor: blue
editor_options: 
  chunk_output_type: inline

---
  
  ```{r setup, include=F, warning=F}
rm(list=ls()) 

library(cjpowR)
library(dplyr)
library(broom)
library(margins)
library(cregg)
library(ggplot2)
library(mlogit)
library(survey)
library(psych)
library(knitr)

```

# Research questions 

**RQ1**: Does FDA approval influence the adoption of new mHealth apps (compared to non-FDA assessed apps) for tracking metabolic health?
  
  # Conjoint experiment set up
  
  ## Conjoint attributes & design
  
  **FDA Approval**: 
  
  - Yes: Has been regulated and approved by the FDA (Food & Drug Administration).
  - No: Has not been assessed by the FDA (Food & Drug Administration)

**Health Benefit**: 
  
  - High: Regular users see a large benefit in metabolic health.
  - Low: Regular users see a small benefit in metabolic health.

**Privacy**: 
  
  - High: Very unlikely to sell data to third-party companies without additional consent.
  - Low: Likely to sell data to third-party companies without additional consent.

**Invasiveness**:
  
  - High: Requires wearing a continuous glucose monitor (CGM), with a microneedle in the arm.
  - Low: Does not require wearing a continuous glucose monitor (CGM), with a microneedle in the arm. 

**Burden**: 
  
  - High: Requires manually logging meal ingredients in a food diary.
  - Low:  Requires taking photos of meals to automatically track foods


-----------------------------------
  **Uniform attribute random sampling**
  
  - 16 trials; randomly sampled 2 of the 32 possible combinations 
  - Random attribute ordering per participant (1-5 per participant but not per choice)
  - Forced choice (logistic outcome)
  
  
   # Results 

   ## H1: 

   **H1** FDA approval will have a significant positive effect on mHealth app choice relative to non-FDA assessed 
   apps. 


```{r, warning=F, message=FALSE}
df <- read.csv("~/Documents/Conjoint/final_combined_df.csv", stringsAsFactors = FALSE)

df$choice_n <- as.numeric(ifelse(df$choice == "yes", 1, 0))  # Convert to binary

df$FDA_Approval <- factor(df$FDA_Approval, levels = c("FDA not approved", "FDA approved"))
df$Burden <- factor(df$Burden, levels = c("low burden", "high burden"))
df$Privacy <- factor(df$Privacy, levels = c("no privacy", "yes privacy"))
df$Invasive <- factor(df$Invasive, levels = c("CGM not required", "CGM required"))
df$Benefit <- factor(df$Benefit, levels = c("small benefit", "large benefit"))

model1 <- amce(df, choice_n ~ FDA_Approval + Burden + Privacy + Invasive + Benefit,id = ~ ResponseId)

model_tibble <- model1 %>% as_tibble() %>%
  filter(!is.na(lower))

# Display the resulting tibble
kable(model_tibble)

library(ggplot2)
library(dplyr)

# Custom labels for attribute levels
custom_labels <- c(
  "FDA not approved" = "Not Approved",
  "FDA approved" = "Approved",
  "low burden" = "Low Burden",
  "high burden" = "High Burden",
  "no privacy" = "No Privacy",
  "yes privacy" = "Privacy",
  "CGM not required" = "No CGM",
  "CGM required" = "CGM Required",
  "small benefit" = "Small Benefit",
  "large benefit" = "Large Benefit"
)

# Create contrast plot with larger font and custom labels
ggplot(model_tibble, aes(x = level, y = estimate, ymin = lower, ymax = upper, color = level)) +
  geom_pointrange(size = 1) +  # Adjust point and line size
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Zero effect line
  coord_flip() +  # Flip for better readability
  theme_minimal(base_size = 14) +  # Set base font size
  labs(
    title = "Contrast Effects of Attributes on Choice",
    x = "Attributes",
    y = "AMCE Estimate"
  ) +
  scale_x_discrete(labels = custom_labels) +  # Apply custom labels
  theme(
    axis.text.y = element_text(size = 16),  # Increase font size of attribute labels
    axis.text.x = element_text(size = 14),  
    plot.title = element_text(size = 18, face = "bold"),  # Larger title
    legend.position = "none"  # Remove legend
  )
```


# Power Analysis 

  Based on these preliminary findings: 

* H1.To detect an AMCE of 0.16, with a power of 0.95, approx. **495** participants are needed.

```{r warning=F, message=FALSE}

rq1pwr = cjpowr_amce(amce = 0.16, power = 0.95, levels = 2)
round(rq1pwr$n, digits =0)  #495
```


